---
title: "Local Fill Dashboard"
resource_files:
- inc/hana_logo_small.png
- Landlord_Report.Rmd
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    theme: readable
    logo: inc/hana_logo_small.png
    css: inc/corp-styles.css
    self_contained: yes
    vertical_layout: fill
    horizontal_layout: fill
    includes:
      before_body: "inc/google-analytics.js"

---


```{r setup, include=FALSE}
library(flexdashboard) 
library(flextable)
library(dplyr)
library(tidyr)
library(rpivotTable)
library(DT)
library(ggplot2)
library(plotly)
library(summarywidget)
library(RiHana)



#########Get Report Data############################
#All data reading and transformations are done in Weekly_Reports_data_gen.R script.
#Here we just load the tables we need.

load("inc/local_fill_dashboard.RData")


closed_30_days<-pipeline_deals %>% filter(close_date>=RiHana::get_relevant_date()$past_30_days,pipeline_stage=='Closed Won') %>% summarise(deals=n())
deals_30_days<-pipeline_deals %>% filter(create_date>=RiHana::get_relevant_date()$past_30_days) %>% summarise(deals=n())
top_unit_30_days<-pipeline_deals %>% filter(create_date>=RiHana::get_relevant_date()$past_30_days) %>% group_by(hana_unit) %>%  summarise(deals=n()) %>% arrange(desc(deals)) %>% slice(1)

pipeline_detail_data<-reactive({
  deals_data<-pipeline_deals %>%
    #move this to extract so it will apply everywhere - not sure why this changed?
#    mutate(close_date=lubridate::as_date(close_date)) %>% 
    mutate(close_date=ifelse(grepl('closed',pipeline_stage,ignore.case = TRUE),close_date,NA),
           close_date=lubridate::as_date(close_date)) %>% 
    filter(between(close_date,input$detail_date[1],input$detail_date[2]) | is.na(close_date),
           grepl(paste0(input$detail_pipeline,collapse = "|"),pipeline_stage),
           grepl(paste0(input$detail_region,collapse = "|"),hana_region),
           grepl(paste0(input$detail_location,collapse="|"),hana_unit),
           grepl(paste0(input$detail_sales,collapse="|"),sales_channel),
           grepl(paste0(input$detail_acquisition,collapse="|"),acquisition_channel),           
           grepl(paste0(input$detail_product,collapse="|"),hana_product)) %>% 
    mutate(monthly_amount=scales::dollar(monthly_amount)) %>% 
        select(-hana_region,-hana_city,-create_week,-create_month,-create_quarter,-acquisition_channel,-acquisition_source,-digital_channel,-sales_channel,-closed_lost_reason,-total_deal_amount,-close_week,-close_month,-close_quarter,-cohort_week,-cohort_month,-cohort_quarter) %>% 
    arrange(desc(pipeline_stage))
  
shiny::validate(
    shiny::need(nrow(deals_data)>0, 
         "No opportunities fit your selected criteria")
  )

  
  return(deals_data)
}
)

trend_data<-reactive({
   trend_data<-pipeline_deals %>% 
     filter(create_date>=input$trend_date[1],
            create_date<=input$trend_date[2],
            grepl(paste0(input$trend_region,collapse = "|"),hana_region),
            grepl(paste0(input$trend_location,collapse="|"),hana_unit),
            grepl(paste0(input$trend_product,collapse="|"),hana_product),
            grepl(paste0(input$trend_acquisition,collapse="|"),acquisition_channel,ignore.case = TRUE)) %>% 
     mutate(timespan=case_when(
           input$TrendTimeDimension=='Week'~create_week,
           input$TrendTimeDimension=='Month'~create_month,
           input$TrendTimeDimension=='Quarter'~create_quarter)) %>% 
    group_by(timespan,hana_product) %>% 
     summarise(opptys=n())

   
  return(trend_data)
}
)

close_data<-reactive({
  close_data<-pipeline_deals %>% 
     filter(pipeline_stage=='Closed Won',
            close_date>=input$trend_date[1],
            close_date<=input$trend_date[2],
            grepl(paste0(input$trend_region,collapse = "|"),hana_region),
            grepl(paste0(input$trend_location,collapse="|"),hana_unit),
            grepl(paste0(input$trend_product,collapse="|"),hana_product),
            grepl(paste0(input$trend_acquisition,collapse="|"),acquisition_channel,ignore.case = TRUE)) %>% 
    mutate(timespan=case_when(
    input$TrendTimeDimension=='Week'~lubridate::floor_date(close_date,unit="week",week_start=1),
    input$TrendTimeDimension=='Month'~lubridate::floor_date(close_date,unit="month"),
    input$TrendTimeDimension=='Quarter'~lubridate::floor_date(close_date,unit="quarter"))) %>% 
    group_by(timespan,hana_product) %>% 
    summarise(opptys=n())
    
  
  return(close_data)
    
  
})

funnel_data<-reactive({
   funnel_data<-pipeline_deals %>% 
     filter(create_date>=input$trend_date[1],
            create_date<=input$trend_date[2],
            grepl(paste0(input$trend_region,collapse = "|"),hana_region),
            grepl(paste0(input$trend_location,collapse="|"),hana_unit),
            grepl(paste0(input$trend_product,collapse="|"),hana_product),
            grepl(paste0(input$trend_acquisition,collapse="|"),acquisition_channel,ignore.case = TRUE),
           !grepl('closed',pipeline_stage,ignore.case = TRUE)) %>% 
#            pipeline_stage %in% c("Pre-funnel","Working to Contact","Deal Qualifying","Touring","Negotiation/Proposal","Contract Sent")) %>% 
#     mutate(pipeline_stage=factor(pipeline_stage,levels=c("Upper Funnel","Qualified - Local Fill Opportunity","Touring", "Negotiation/Proposal","Contract Sent", "Closed Lost", "Closed Won")))  %>%    
     mutate(pipeline_stage=factor(pipeline_stage,levels=c("Exploratory","Qualified","Touring / Solutioning","Negotiation","Proposal","Verbal Award / Contract Sent")))  %>%    
      arrange(pipeline_stage) %>% 
     group_by(pipeline_stage) %>% 
     summarise(opptys=n())

  return(funnel_data)
}
)


conversion_data<-reactive({
  conversion_data<-historical_deal_stage %>% 
    filter(create_date>=input$trend_date[1],
           create_date<=input$trend_date[2],
            grepl(paste0(input$trend_region,collapse = "|"),hana_region),
            grepl(paste0(input$trend_location,collapse="|"),hana_unit),
            grepl(paste0(input$trend_product,collapse="|"),hana_product),
            grepl(paste0(input$trend_acquisition,collapse="|"),acquisition_channel,ignore.case = TRUE)) %>% 
    select(deal_id,Pipeline_resolution,pipeline_stage) %>%
    filter(Pipeline_resolution %in% c('Closed Lost','Closed Won')) %>%
    unique(.) %>%
    group_by(pipeline_stage,Pipeline_resolution) %>%
    summarise(deals=n()) %>%
    pivot_wider(names_from=c(Pipeline_resolution),
              values_from = c(deals),
              values_fill = list(deals=0)) %>%
    janitor::clean_names(.)  %>%
    ungroup(.) %>%
    mutate(conversion=closed_won/(closed_won+closed_lost),
         pipeline_stage=factor(pipeline_stage,levels=c("Interest Expressed","Potential Opportunity","Initial Terms Sent", "Working to Contact","Deal Qualifying","Touring","Negotiation/Proposal","Contract Sent","Closed Lost","Closed Won","Cold/Dead"))) %>%
#     pipeline_stage=factor(pipeline_stage,levels=c("Exploratory","Qualified","Touring / Solutioning","Negotiation","Proposal","Verbal Award / Contract Sent")))  %>%    
  arrange(pipeline_stage)

  
  return(conversion_data)
  
})
  

time_in_stage_data<-reactive({
  
  time_in_stage_data<-historical_deal_stage %>% 
    filter(create_date>=input$trend_date[1],
           create_date<=input$trend_date[2],
            grepl(paste0(input$trend_region,collapse = "|"),hana_region),
            grepl(paste0(input$trend_location,collapse="|"),hana_unit),
            grepl(paste0(input$trend_product,collapse="|"),hana_product),
            grepl(paste0(input$trend_acquisition,collapse="|"),acquisition_channel,ignore.case = TRUE),
           grepl(input$trend_resolution,Pipeline_resolution,ignore.case = TRUE),
           !grepl('closed',pipeline_stage,ignore.case=TRUE))

  return(time_in_stage_data)
  
})
```


Summary
===================================== 

Column {data-width=70%} 
-------------------------------------

### Summary

```{r}

big_border = officer::fp_border(color="black", width = 2)
border_v = officer::fp_border(color="gray")
border_h = officer::fp_border(color="gray")

#myft <- flextable(pipeline_summary %>% arrange(hana_unit,measure))
myft <- flextable(pipeline_summary)
myft <- align(myft, align = "top", part = "all")
myft <- border_inner_h(myft, part="all", border = border_h )
myft <- border_inner_v(myft, part="all", border = border_v )
myft <- merge_v(myft,j="hana_unit")
myft <- autofit(myft)
myft <- fix_border_issues(myft)
myft
```




Column {data-width=25%} 
-------------------------------------

###### **Data Updated:** _`r file.info('inc/local_fill_dashboard.RData')$mtime` ._


Over the past 30 days, **`r deals_30_days$deals`** deals have been created. <br>

For deals created over that time,**`r closed_30_days$deals`** have been won, for a close rate of **`r scales::percent(closed_30_days$deals/deals_30_days$deals)` **. <br>

**`r top_unit_30_days$hana_unit`** has the most deals created in the past month, with **`r top_unit_30_days$deals`**.


Fill Pivot
===================================== 

### Fill Overview

```{r}


renderRpivotTable({

  pivot_data<-pipeline_deals %>% 
    select(deal_name,customer_name,hana_region,hana_unit,hana_city,hana_product,pipeline_stage,create_date,create_month,seats,lease_term,
         monthly_amount,total_deal_amount,close_date,close_month,cohort_month,acquisition_channel,acquisition_source,digital_channel,
         sales_channel,pipeline_stage_detail,last_pipeline_stage) %>%                  
  replace_na(list(monthly_amount=0,digital_channel="N/A",last_pipeline_stage="N/A")) %>%
  drop_na() 

  rpivotTable(data=pivot_data, cols = "pipeline_stage",rows=c("hana_unit","hana_product"),sorters = "function(attr) {
    var sortAs = $.pivotUtilities.sortAs;
    if (attr == \"pipeline_stage\")
        { return sortAs([\"Exploratory\", \"Qualified\", \"Touring / Solutioning\", \"Negotiation\",\"Proposal\", \"Verbal Award \ Contract Sent\", \"Closed Won\", \"Closed Lost\"]);  }
    }")

  })

```


Fill Trends {data-orientation=rows}
===================================== 

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}

dateRangeInput('trend_date',
      label = 'Choose the time range',
      min=RiHana::get_relevant_date()$yoy_date,
      max=RiHana::get_relevant_date()$yesterdays_date,
      start = RiHana::get_relevant_date()$yoy_date, 
      end = RiHana::get_relevant_date()$yesterdays_date,
      weekstart = 1
    )

radioButtons("TrendTimeDimension",label="Pick the time interval",
             choices=c("Week",
                       "Month",
                       "Quarter"),
             selected="Month"
            )
helpText("Note: Time interval specifies the X axis where appicable for trending data")



selectizeInput(
        'trend_region', 'Choose a Region', choices = unique(na.omit(pipeline_deals$hana_region)),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)


selectizeInput(
        'trend_location', 'Choose a Location', choices = unique(na.omit(pipeline_deals$hana_unit)),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)

selectInput(
"trend_product",
label = "Product",
choices=c("All"="*",
          "Team"="Team",
          "Share"="Share",
          "Meet"="Meet"),
selected="All",
multiple = TRUE
)


selectInput(
"trend_acquisition",
label = "Acquisition Channel",
choices=c("All"="*",
          "Marketing"="Marketing",
          "Broker"="Broker",
          "Local Sales"="Local",
          "Enterprise"="Enterprise"),
selected="All",
multiple = TRUE
)

selectInput(
"trend_resolution",
label = "Final Deal State",
choices=c("All"="*",
          "Won"="won",
          "Lost"="lost",
          "In progress"="in progress"),
selected="All",
multiple = FALSE
)

helpText("Note: Final Deal State can be used to filter deals in the Time in Stage box plot.")


```

Row {data-height=400}
-------------------------------------

### Opportunities Created Over Time

```{r}

 renderPlotly({
   opptys_data<-trend_data()
  plot_ly(opptys_data,
          color=~hana_product,
          colors=hana_color_palette(n_distinct(opptys_data$hana_product),2),
          x = ~timespan,
          y = ~opptys,
          type="bar")%>%
    layout(barmode = "stack",
           bargap=0.1,
           legend = list(orientation = 'h'))
}
)
```

### Opportunities Won Over Time

```{r}

 renderPlotly({
   won_opptys_data<-close_data()
  plot_ly(won_opptys_data,
          color=~hana_product,
          colors=hana_color_palette(n_distinct(won_opptys_data$hana_product),2),
          x = ~timespan,
          y = ~opptys,
          type="bar")%>%
    layout(barmode = "stack",
           bargap=0.1,
           legend = list(orientation = 'h'))
}
)
```


Row 
-------------------------------------

### Local Fill Funnel

```{r}

 renderPlotly({
   funnel_data<-funnel_data()

  plot_ly(funnel_data,
          marker = list(color = "#002D36"),
          x = ~opptys,
          y = ~pipeline_stage,
          type="funnel")
    
 }
 )

```

### Conversion Baseline

```{r}

renderPlotly({
   conversion_data<-conversion_data()
  plot_ly(conversion_data,
          marker = list(color = "#002D36"),
          orientation='h',
          y = ~pipeline_stage,
          x = ~conversion,
          bargroupgap=0.1,
          bargap = 0.15)%>%
    highlight('plotly_click',color='red') %>% 
    layout(xaxis = list(tickformat = "%"))
})
  
```

### Time in Funnel Stage

```{r}

 renderPlotly({
   time_in_stage_data<-time_in_stage_data()


time_in_stage_data %>% 
plot_ly(y = ~time_in_stage, 
        color = ~pipeline_stage, 
        colors=hana_color_palette(n_distinct(historical_deal_stage$pipeline_stage)),
        type = "box") %>% 
  layout(showlegend = FALSE)

 }
 )

```


Fill Detail {data-orientation=rows}
===================================== 

Inputs {.sidebar}
-----------------------------------------------------------------------
```{r}


dateRangeInput('detail_date',
      label = 'Choose the time range',
      min=RiHana::get_relevant_date()$yoy_date,
      max=RiHana::get_relevant_date()$yesterdays_date,
      start = RiHana::get_relevant_date()$ytd_date, 
      end = RiHana::get_relevant_date()$yesterdays_date,
      weekstart = 1
    )

helpText("Note: this will apply a filter for deals that have a closed status.  It will not affect current open deals.")



# selectInput(
# "detail_pipeline",
# label = "Pipeline Stage",
# choices = c("All" ="*",
#             "Pre-funnel"="Pre-funnel",
#             "Working to Contact"="Working to Contact",
#             "Deal Qualifying"="Deal Qualifying",
#             "Touring"="Touring",
#             "Negotiation/Proposal"="Negotiation/Proposal",
#             "Contract Sent"="Contract Sent",
#             "Closed Lost"="Closed Lost",
#             "Closed Won"="Closed Won"),
# selected = c("All"),
# multiple = TRUE
# )

selectizeInput(
        'detail_pipeline', 'Choose a Stage', choices = unique(pipeline_deals$pipeline_stage),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)


selectizeInput(
        'detail_region', 'Choose a Region', choices = unique(na.omit(pipeline_deals$hana_region)),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)

selectizeInput(
        'detail_location', 'Choose a Location', choices = unique(na.omit(pipeline_deals$hana_unit)),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)

selectInput(
"detail_product",
label = "Product",
choices=c("All"="*",
          "Team"="Team",
          "Share"="Share",
          "Meet"="Meet"),
selected="All",
multiple = TRUE
)

selectInput(
"detail_sales",
label = "Sales Channel",
choices=c("All"="*",
          "Local"="Local",
          "Broker"="Broker",
          "Enterprise"="Enterprise"),
selected="All",
multiple = TRUE
)

selectizeInput(
        'detail_acquisition', 'Choose Acquisition Channel(s)', choices = unique(pipeline_deals$acquisition_channel),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)

radioButtons("detail_confidential_client",label="Hide confidential client names?",
             choices=c("No"="no",
                       "Yes"="yes"),
             selected="no")
helpText("Note: The confidential client flag has not been migrated to Simplify.  This functionality will be enabled again once supported in Simplify.")
```

To download this data in the Landlord Report format, click:

```{r}
downloadButton('report', label='Landlord Report')

downloadHandler(filename = function() { 
    return('report.html')

 }, content = function(file) {
        # Copy the report file to a temporary directory before processing it, in
        # case we don't have write permissions to the current working dir (which
        # can happen when deployed).
        tempDirectory<-tempdir()
        tempReport <- file.path(tempDirectory, "Landlord_Report.Rmd")
        tempHeader <- file.path(tempDirectory,"hana_logo_small.png")
        file.copy("Landlord_Report.Rmd", tempReport, overwrite = TRUE)
        file.copy("inc/hana_logo_small.png", tempHeader, overwrite = TRUE)

        # Set up parameters to pass to Rmd document
       # params <- list(deal_file = pipeline_detail_data())

        # Knit the document, passing in the `params` list, and eval it in a
        # child of the global environment (this isolates the code in the document
        # from the code in this app).
        rmarkdown::render(tempReport, output_file = file,
          params = params
#          envir = new.env(parent = globalenv())
        )
}
    )


```


Row 
-------------------------------------

```{r ny summary, echo=FALSE, message=FALSE, warning=FALSE, results='asis', out.width = "80%",fig.asp = .30}

DT::renderDataTable(server = FALSE,{
  datatable(cbind(' ' = '&oplus;', pipeline_detail_data()), escape = FALSE, extensions = c('Scroller','Buttons', 'ColReorder'), 
            fillContainer = TRUE,
          options = list(scrollY = 800, 
                         scroller = TRUE, 
                         colReorder=TRUE,
                         dom = 'tB',
                         buttons = c('csv'),
                         columnDefs = list(list(visible = FALSE, searchable=FALSE, targets = c(13,14,15,16)),
      list(orderable = FALSE, className = 'details-control', targets = 1))),
            callback = JS("
  table.column(1).nodes().to$().css({cursor: 'pointer'});
  var format = function(d) {
    return '<div style=\"background-color:#eee; padding: .5em;overflow-wrap: break-word;\"> Status Last Week: ' +
    d[14] +
    '<br/>Status This Week: ' +
    d[13] +
    '<br>Link to CRM: ' +
    d[15] +
    '<br/>Notes: ' +
            d[16]  + '</div>';
  };
  table.on('click', 'td.details-control', function() {
    var td = $(this), row = table.row(td.closest('tr'));
    if (row.child.isShown()) {
      row.child.hide();
      td.html('&oplus;');
    } else {
      row.child(format(row.data())).show();
      td.html('&CircleMinus;');
    }
  });")
  )
}
)


```


